A Natural Language Processing Approach for the Digitalization of Roaming Agreement

### 2021-09-05 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/DesignedMethodology.tex
05.08.21.1

\section{NLP Engine methodology}\label{methodology}
In general, our design consists of the following two approaches (which we discuss in more detail in this section): \textit{detection} and \textit{comparison}. While \textit{detection} has symbols as basic processing unit, \textit{comparison} has sub-articles as basic processing unit. \textit{Detection} represents the capability to detect \textit{variables} in a text file, i.e., the RA. For this purpose, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content of text documents by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.

\textit{Comparison} represents the capability to find \textit{similarities} and differences between the sub-articles present in the RA concerning the sub-articles present in the GSMA standard template. In this regard, \textit{text similarity} constitutes the enabling technology of the \textit{comparison} approach, since it is a resource commonly used for pattern classification, clustering, and information retrieval problems \cite{7429408}. We employ \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}. As a result of the \textit{comparison}, it is determined that while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the RA) represents a \textit{customized text}. Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles, and the existing differences are given by the presence of \textit{variables} such as the commercial names of MNOs and the start date of the RA. The next section integrates tools, NLP techniques, and text processing techniques as part of the designed methodology.

@@

The \textit{detection} phase includes a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API. For this reason, the text is segmented into pieces of 100 symbols. For each symbol chunk the API outputs entities, key phrases and sentiment in JavaScript Object Notation (JSON) format \cite{AWS2021}, which must be grouped and further processed. The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech', and 'Tag'. In turn, it adds to these the 'Frequency' field that indicates the number of repetitions of entities with same the same name, i.e., the same 'Text' field. Once this filtering has been done, entities are sorted according to a logic that defines their relevance degree. The designed logic is particularized according to the type of \textit{variable} to be detected. For instance, for the name of the MNO, the 'Score', 'Frequency', and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases. The detected \textit{variables} are stored to be used later to determine which ones are part of the \textit{variations} or \textit{customized texts}.

>>>>

\section{NLP Engine methodology}\label{sec:methodology}
In general, our design consists of the following two approaches (which we discuss in more detail in this section): \textit{detection} and \textit{comparison}. While \textit{detection} has symbols as basic processing unit, \textit{comparison} has sub-articles as basic processing unit. \textit{Detection} represents the capability to detect \textit{variables} in a text file, i.e., the RA. For this purpose, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content of text documents by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text~\cite{AWS2021}.

\textit{Comparison} represents the capability to find \textit{similarities} and differences between the sub-articles present in the RA concerning the sub-articles present in the GSMA standard template. In this regard, \textit{text similarity}~\cite{Deza2009} constitutes the enabling technology of the \textit{comparison} approach, since it is a resource commonly used for pattern classification, clustering, and information retrieval problems~\cite{7429408}. We employ \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets~\cite{Gupta2018}. As a result of the \textit{comparison}, it is determined that while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the RA) represents a \textit{customized text}. Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles, and the existing differences are given by the presence of \textit{variables} such as the commercial names of MNOs and the start date of the RA. The next section integrates tools, NLP techniques, and text processing techniques as part of the designed methodology.

@@

The \textit{detection} phase includes a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API. For this reason, the text is segmented into pieces of 100 symbols. For each symbol chunk the API outputs entities, key phrases and sentiment in JavaScript Object Notation (JSON) format~\cite{AWS2021}, which must be grouped and further processed. The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech', and 'Tag'. In turn, it adds to these the 'Frequency' field that indicates the number of repetitions of entities with same the same name, i.e., the same 'Text' field. Once this filtering has been done, entities are sorted according to a logic that defines their relevance degree. The designed logic is particularized according to the type of \textit{variable} to be detected. For instance, for the name of the MNO, the 'Score', 'Frequency', and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases. The detected \textit{variables} are stored to be used later to determine which ones are part of the \textit{variations} or \textit{customized texts}.

### 2021-09-05 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Introduction.tex
05.08.21.1

%{\color{red}The remainder of this paper is organised as follows: we briefly review existing work in Section~\ref{existing}, we describe our methods in details in Section~\ref{methods}, we then present and discuss our results in Section~\ref{results}, followed by conclusions and ideas for future work in the last section.}

>>>>

\textcolor{blue}{The remainder of this paper is organised as follows: we briefly review existing work in Section~\ref{sec:related}, we describe our methods in details in Section~\ref{sec:methodology}, we then present and discuss our results in Section~\ref{sec:results}, followed by conclusions and ideas for future work in the last section.}
